\Large{Adversarial Training against Systematic Uncertainty}

### 2016-09-20 tex/paper.tex
Intro from Michael (#5)
* update intro

* adding stuff to intro

>>>>

The discovery of new particles or physical phenomena in high energy
physics experiments, like those at the Large Hadron Collider, 
requires the observation of statistically significant deviations from
the predictions of the Standard Model, the current model
of the known fundamental particles and their interactions.  Typically,
discovery requires satisfying the \textit{5-sigma rule}, 
whereby the deviation must be at least five standard deviations from
predictions, i.e. having a p-value of $p \lesssim 3 \times 10^{-7}$.
The evaluation of the statistical significance must not only account
for statistical uncertainties, but also systematic 
uncertainties that represent our incomplete knowledge of the theory of
particle interactions or of the properties of the experimental
detection apparatus. Systematic uncertainties can alter the expected
rate of signal and background classes, e.g. their priors, as well as
the distributions of features. As such, the signal class true-positive
rate and the background class false-positive rate of a classifier can
change with variations in the systematic uncertainty thereby
decreasing the sensitivity of an analysis.

In this paper, we present a new strategy for training a classifier,
based on adversarial training~\citep{goodfellow2014generative}, 
which aims to build a classifier whose decision function is invariant
under variations due to systematic uncertainties.  In this way,
uncertainties on predictions from simulations will have a reduced
impact when computing the significance of potential deviations after
application of the discriminant model and thereby increase
the sensitivity of the analysis to signals from potential new physics sources.

Given training data $x \in X$ and associated labels $y \in \{s,
b_{i=1...k} \}$ where $s$ is the signal class and $b_{i=1...k}$ are
the background classes, then the probability distribution of the data
can be written
\[
p(x) = \pi_s p(x|y=s) + \sum_{i=1}^{k} \pi_{b_i} p(x | y=b_i)
\]
where $\pi_{y}$ represents the prior for the signal or a given
background, and $p(x|y)$ is the conditional distribution of the data
for the signal or a given background. Systematic uncertainties can
affect this distribution in the following ways:
\begin{itemize}
\item Uncertainties on the priors $\pi_{y}$.  These arise from
  uncertainties on the rates we expect a given process to occur as
  predicted from theoretical calculations or from alternative
  measurements of the rate of a given class.

\item Uncertainties in the simulators of the physical interactions,
  giving rise to uncertainties on the distributions $p(x|y)$.  These
  uncertainty are often determined by comparing the predictions of
  different simulations using differing models of the same physical
  process.

\item Uncertainties on the detection apparatus and it's effect on the
  measurement of particle properties, giving rise to uncertainties on
  the distributions $p(x|y)$.  For instance this includes
  uncertainties on our knowledge of the mean and variance of the
  measured energy distribution of a particle.

\end{itemize}
In this paper, we will not address uncertainties of the first type
mentioned above (uncertainties on the priors).  Rather, we will focus
on mitigating the effect of systematic uncertainties that alter the
conditional distributions $p(x|y)$.

Systematic uncertainties are parameterized by nuisance parameters in
the statistical analysis of data.  Nuisance parameter often, though
not always, have a suitable prior coming from alternative measurements
in data.  For instance, The average measured energy of an electron in
simulation may be compared with those in data using a relatively pure
sample of $Z$ boson decays to electrons.  The average measured
electron energy can not be measured without uncertainty, and the
measured uncertainty can be used in other analyses to estimate the
uncertainty deriving from our imperfect knowledge of the electron's
energy.  A nuisance parameter is assigned to the electron energy
uncertainty, which controls the variation of the electron energy in
the statistical analysis of data.  Nuisance parameters are typically,
though not always, constrained by a suitable prior, e.g. a Gaussian
distribution with a standard deviation equal to the measured uncertainty.
